---
title: "Queen of Hearts Simulation Studies"
author: "Greg Petrucci Jr"
date: "4/5/2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
setwd("/Users/gpetrucci/Box/Petrucci_Personal/Univeristy of Massachusetts/spring.2018/Fun Code/Queen of Hearts Sim")
wd = getwd()
library(tidyverse)
library(stringr)
```

# Introduction
Queen of Hearts is a silly game that is played at the Elks in Norwood, Ma. This is a simulation of the probability of winning during the first week (n=54 cards remain) and 1000 unique participants enter the drawing, each selecting a random number that corresponds to where the Queen of Hearts is on the board, randomly from 1 through 54. 

# Methods

```{r, Making the deck of cards}

#Here I make the deck of cards
set.seed(886600) 
buildDeck <- function(noOfDecks=1){
  suits <- c("Clubs", "Spades", "Diamonds", "Hearts")
  cards <- c("Ace", 2:10, "Jack", "Queen", "King")
  Deck <- paste(cards, rep(suits, each = 13), sep = "-")
  Deck <- as.data.frame(Deck)
  Joker <- c("Joker")
  Jokers_In <- as.data.frame(paste(rep(Joker, 2)))
  names(Jokers_In) <- "Deck"
  Full_Deck <- rbind(Deck, Jokers_In, stringsAsFactors = F)
  d <- rep(Full_Deck, noOfDecks) #Build decks
  shuffledDeck <- sample(d, length(d)) #Shuffle decks
  return(as.data.frame(shuffledDeck))
}
deck <- buildDeck(1)
deck <- deck[sample(1:nrow(deck)),]
deck <- as.data.frame(deck)
queen_of_hearts_number <- 40
```

## In the code above I simulate a deck of cards.

```{r, Function for Making the weekly name entry and their respective card number}
#Here I make a function for weekly name entry and column 
#2 is the corresponding card number for that participant
weeklyName_Entry <- function(n=1000){
  names <- c(rep("Greg", n ))
  for (i in 1:length(names)){
    names[i] <-paste(names[i], i, sep="") 
  }
  names<- as.data.frame(names)
  names$card_number <- NA
  for ( i in 1:nrow(names)){
    names$card_number[i] <- sample(1:54, 1)
  }
  
  return(names)  
}

week1_names <- weeklyName_Entry(n=1000)

```

##Output from above is week1_names which has 1000 names and random numbers ranging from 1 through 54. This represents 1000 unique names entering the drawing in week one and each of the choose a random card number from 1 through 54.

```{r, Function for testing if the randomly sampled name is same as the criterion name}

set.seed(Sys.time())

weekly_drawing_for_names_and_queen <- function(week1_names){ 
  #This function evaluates if the true name is slected 
  #from the fish bowl, if yes, counter = 0, else counter = 1
  
    week1_name_winner_index <- sample(1:nrow(week1_names), 1)
    week_1_criterion <- week1_names[week1_name_winner_index,] 
  
    drawing_winner_index <- sample(nrow(week1_names), 1)
    
    if (week1_names[drawing_winner_index,][1,1] == week_1_criterion[1,1]){ 
      #check to see if the name hits
      counter_name <- 0
    } else {
      counter_name <- 1
    }
  
    if(week1_names[drawing_winner_index,][,2]== 40){ 
      #check to see if the queen of hearts numbers hit
    counter_queen <- 0
    } else {
    counter_queen <-1
  }
    
  return(c(counter_name, counter_queen)) 
    # double 0 denotes hitting both 
    #names and queen of hearts number
}


```

##Code above is a function which evaluates the following:
 
 1.) Sampled from 1 through all names that entered in week 1 randomly select a participant to represent the winner. I have to do this because in real life there is a winner that is picked. Here, week_1_criterion represents what we will call the truth for week 1.
 
2.) Next, I randomly sample from all the names that entered in week 1 and denote this person as the person who has their name drawn.

3.) Next I check to see if the name that was randomly selected is the same as the criterion; this step represents "your" card being chosen from the bin of names.

4.) Finally, we need to check that the number you had on your card is the same as the week of hearts. This would represent you being a "winner, winner"; your name was drawn and you had the correct card number corresponding to the queen of hearts.


```{r}
INF <- 100000
two_pull_results <- matrix(NA, nrow=INF, ncol=3)
colnames(two_pull_results) <- c("First_Pull", "Second_Pull", "Sum")

for (i in 1:INF){
  two_pull_results[i,1] <- weekly_drawing_for_names_and_queen(week1_names) [1]
  two_pull_results[i,2] <- weekly_drawing_for_names_and_queen(week1_names) [2]
  two_pull_results[i,3] <-  two_pull_results[i,1] + two_pull_results[i,2]
}


```

##The code above simulates 100000 trials at "week 1" (all n=54 cards remain on the board) where there are 1000 unique particpants entered into the contest, each randomly selected one number from 1 through 54. The outcome of interest is having your name selected and the number you selected equal to the card number for the queen of hearts. 


##Based on 100000 simulations the probability of winning one week 1 is  approximately .00003.

```{r}

two_pull_results <- as.data.frame(two_pull_results)
ggplot(two_pull_results, aes(First_Pull, Second_Pull)) + 
  geom_jitter() + 
  labs(title="Probability of Winning on Both Draws Based on 100000 Simulations" , x="Your Name Was Drawn", y ="You Picked the Card Number for the Queen of Hearts" ) +
  scale_x_discrete(limits=c(0,1), labels=c("TRUE", "False")) +
    scale_y_discrete(limits=c(0,1), labels=c("TRUE", "False")) 
```
 
 